### 2012-04-30 GUIErrorDetector/paper/technique.tex
address reviewers' comments

\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
thread is spawned by the UI thread. Under this assumption,
we ignore all non-UI threads created by the GUI framework
before the UI thread has been initialized. That is, all post-initialization
GUI work occurs in the UI thread. Once the GUI is visible, the
application is driven by events, which are always handled in the UI thread.
We believe this assumption is reasonable, since if a non-UI thread 
spawned during pre-initialization GUI work accesses a GUI object, an exception becomes
immediately apparent and the whole application may abort even before the
GUI is visible. This is highly unlikely for fielded GUI
applications.
}\vspace{1mm}

@@

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a call graph $\mathit{cg}$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\FOR{each $\mathit{expression}$ in $\mathit{P}$}
\IF{isReflectionCall($expression$)}
\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{expression}$)
\STATE $\mathit{newExpr}$ $\leftarrow$ createObjectCreationExpression($\mathit{objectSet}$)
\STATE replace $\mathit{expression}$ with $\mathit{newExpr}$
\ENDIF
\ENDFOR
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\RETURN $\mathit{cg}$
%\ENDWHILE
\end{algorithmic}
\vspace{-3mm}
\caption{A reflection-aware call graph construction algorithm. Lines
1 -- 7 are a simple program transformation to replace reflection calls
with object creations, and line 8 builds the call graph using
an existing call graph construction algorithm. This algorithm
is parameterized by two methods on lines 2 and 3. 
How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
} 
\label{fig:cgalgorithm}
\end{figure}

%GUI applications tend to use reflection intensively. In particular,
GUI applications built on top of the Android framework
use configuration files and reflection to specify GUI layout.
As a result, call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9 -- 11) updates the text.

@@

%\item
\textbf{2. Filter Reports with User-Annotated Methods}. Users are
permitted to explicitly annotate project-specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed. In our experiments, we produced a list of \filternum
annotated methods for two subjects (Fennec and MyTracks) because they use a customized
pattern to interact with the GUI framework.

>>>>

\noindent {\textsc{\textbf{Assumption 2.}}} { We assume that each non-UI
thread is (transitively) spawned by the UI thread. Under this assumption,
we ignore all non-UI threads created by the GUI framework
before the UI thread has been initialized. That is, all post-initialization
GUI work occurs in the UI thread. Once the GUI is visible, the
application is driven by events, which are always handled in the UI thread.
We believe this assumption is reasonable, since if a non-UI thread 
spawned during pre-initialization GUI work accesses a GUI object, an exception becomes
immediately apparent and the whole application may abort even before the
GUI is visible. This is highly unlikely for fielded GUI
applications.
}\vspace{1mm}

@@

\begin{figure}[t]
\vspace{3mm}
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a call graph $\mathit{cg}$\\
\vspace{-4mm}
\begin{algorithmic}[1]
\FOR{each $\mathit{expression}$ in $\mathit{P}$}
\IF{isReflectionCall($expression$)}
\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{expression}$)
\STATE $\mathit{newExpr}$ $\leftarrow$ createObjectCreationExpression($\mathit{objectSet}$)
\STATE replace $\mathit{expression}$ with $\mathit{newExpr}$
\ENDIF
\ENDFOR
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\RETURN $\mathit{cg}$
%\ENDWHILE
\end{algorithmic}
\vspace{-3mm}
\caption{A reflection-aware call graph construction algorithm. Lines
1--7 are a simple program transformation to replace reflection calls
with object creations, and line 8 builds the call graph using
an existing call graph construction algorithm. This algorithm
is parameterized by two methods on lines 2 and 3. 
How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
} 
\label{fig:cgalgorithm}
\end{figure}

%GUI applications tend to use reflection intensively. In particular,
GUI applications built on top of the Android framework
use configuration files and reflection to specify GUI layout.
As a result, call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9--11) updates the text.

@@

%\item
\textbf{2. Filter Reports with User-Annotated Methods}. Users are
permitted to explicitly annotate specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed.

In our experiments, 
we produced a list of \filternum annotated methods for two
subjects (MyTracks and Fennec), since they employ a customized pattern
to interact with the GUI framework. For example, in MyTracks, all non-UI
threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
This method can be invoked from any thread and will never cause an
invalid thread access error, because it checks whether the current
thread is the UI thread or not before execution. If not,
this method will be executed asynchronously via
message passing.

% we produced a list of \filternum
%annotated methods for two subjects (Fennec and MyTracks) because they use a customized
%pattern to interact with the GUI framework.
